\documentclass{article}

\usepackage[english]{babel}
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}\mathtoolsset{showonlyrefs=true}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\usepackage{caption}
\usepackage{subcaption}

\usepackage{dsfont}

% -------------
% Some commands
% -------------

% Environment
\newcounter{rem}
\newtheorem{remark}[rem]{Remark}

\newcounter{th}
\newtheorem{theorem}[th]{Theorem}

\newcounter{scenario}[section]
\newenvironment{scenario}[1][]{\refstepcounter{scenario}\par\medskip
   \noindent \textbf{Scenario~\thescenario. #1} \rmfamily}{\medskip}

\newenvironment{results}[1][]{\noindent \textbf{#1} \rmfamily}{\medskip}

\providecommand{\keywords}[1]{\textbf{\textit{Keywords---}} #1}

% Stats
\newcommand{\EE}{\mathbb{E}} % Expectation
\newcommand{\RR}{\mathbb{R}} % R
\newcommand{\NN}{\mathbb{N}} % N
\newcommand{\XX}{\mathcal{X}} % set X
\newcommand{\dd}{{\rm d}}

% Spaces
\newcommand{\TT}[1]{\mathcal{T}_{#1}} % Domain definition space
\newcommand{\sLp}[1]{\mathcal{L}^{2}\left(#1\right)} % L^p space
\newcommand{\HH}{\mathcal{H}} % Product of L^p space
\newcommand{\GG}{\mathcal{G}} % (L^p)^N space

% Inner product and norm
\newcommand{\pointt}{\mathbf{t}} % Indexed of multivariate curves
\newcommand{\points}{\mathbf{s}} % Indexed of multivariate curves
\newcommand{\inLp}[2]{\left\langle#1, #2\right\rangle} % Inner product in Lp
\newcommand{\inR}[2]{\left(#1, #2\right)}
\newcommand{\inRM}[2]{\left(#1, #2\right)_{\mathbf{M}}}
\newcommand{\normLp}[1]{\left|\!\left|#1\right|\!\right|} % Norm in Lp
\newcommand{\normR}[1]{\left(\!\left(#1\right)\!\right)} %
\newcommand{\normRM}[1]{\left(\!\left(#1\right)\!\right)_{\mathbf{M}}} %
\newcommand{\inH}[2]{\langle\!\langle#1, #2\rangle\!\rangle}
\newcommand{\inHw}[2]{\langle\!\langle#1, #2\rangle\!\rangle_w}
\newcommand{\inHG}[2]{\langle\!\langle#1, #2\rangle\!\rangle_\Gamma}
\newcommand{\normH}[1]{\left|\!\left|\!\left|#1\right|\!\right|\!\right|}
\newcommand{\normHG}[1]{\left|\!\left|\!\left|#1\right|\!\right|\!\right|_\Gamma}

% Data/Process related
\newcommand{\Xnp}{X_n^{(p)}} % Observation n, feature p
\newcommand{\Xnq}{X_n^{(q)}} % Observation n, feature q
\newcommand{\hatXnp}{\widehat{X}_n^{(p)}} % Reconstruction
\newcommand{\Xp}[1]{X^{(#1)}} % Feature p
\newcommand{\mup}[1]{\mu^{(#1)}} % Feature p
\newcommand{\fp}{f^{(p)}} 
\newcommand{\gp}{g^{(p)}}

% Geometric related
\newcommand{\pobs}[1]{\mathrm{#1}} % Point related to observations
\newcommand{\CN}{\mathcal{C}_{\!N}} % Cloud of features
\newcommand{\Gmu}{\pobs{G}_{\!\mu}} % Centre of gravity of C_N
\newcommand{\OH}{\pobs{O}_{\!\mathcal{H}}} % Centre of H

\newcommand{\pfea}[1]{\mathsf{#1}} % Point related to features
\newcommand{\CP}{\mathcal{C}_{\!P}} % Cloud of observations
\newcommand{\Gfea}{\pfea{G}_{\!\mu}} % Centre of gravity of C_P
\newcommand{\OG}{\pfea{O}_{\!\RR}} % Centre of H

% Declaration of math operator
\DeclareMathOperator{\Var}{Var}
\DeclareMathOperator{\Cov}{Cov}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator{\bigO}{\mathcal{O}}

% Function subset restriction  
\newcommand\restr[2]{{ %
  \left.\kern-\nulldelimiterspace  %
  #1  %
  \vphantom{\big|}  %
  \right|_{#2}  %
}}
% -------------

\title{On the estimation of the number of components in multivariate functional principal component analysis}
\author{%
Steven Golovkine\thanks{MACSI, Department of Mathematics and Statistics, University of Limerick, Ireland \href{mailto:steven.golovkine@ul.ie}{steven.golovkine@ul.ie}}
\and
Edward Gunning\thanks{MACSI, Department of Mathematics and Statistics, University of Limerick, Ireland \href{mailto:edward.gunning@ul.ie}{edward.gunning@ul.ie}}
\and
Andrew J. Simpkin\thanks{School of Mathematical and Statistical Sciences, University of Galway, Ireland \href{mailto:andrew.simpkin@nuigalway.ie}{andrew.simpkin@nuigalway.ie}}
\and
Norma Bargary\thanks{MACSI, Department of Mathematics and Statistics, University of Limerick, Ireland \href{mailto:norma.bargary@ul.ie}{norma.bargary@ul.ie}}
}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\cite{happMultivariateFunctionalPrincipal2018} developed a methodology for multivariate functional data analysis for data observed on different dimensional domains. It relies on an estimation of principal components for each univariate feature. In this paper, we propose extensive simulations to estimate the number of components. We empirically show that this estimated number may be unreliable, and thus we advise practitioners to be careful when choosing it.
\end{abstract}

% MAIN --------
\input{main/main}

% \input{main/introduction}

% \input{main/ideas}
% -------------

% ACKNOWLEDGMENT -------
\section*{Acknowledgment}

S. Golovkine, A. J. Simpkin and N. Bargary are partially supported by Science Foundation Ireland under Grant No. 19/FFP/7002 and co-funded under the European Regional Development Fund. E. Gunning is supported in part Science Foundation Ireland (Grant No. 18/CRT/6049) and co-funded under the European Regional Development Fund. The authors also wish to acknowledge the Irish Centre for High-End Computing (ICHEC) for the provision of computational facilities and support.

\bibliographystyle{plainnat}
\bibliography{./biblio}

\end{document}

