%!TEX root=../main.tex
\section{Introduction} % (fold)
\label{sec:introduction}

We aim to show that the procedure proposed by \cite{happMultivariateFunctionalPrincipal2018a} may leaad to inconsistency in the retained number of components, based on extensive simulation.

The simulation may varies has follow:
\begin{itemize}
    \item Number of curves $N = 25, 50, 100, 200$
    \item Number of sampling points $M = 25, 50, 100, 200$
    \item Number of components $P = 2, 5, 10, 20, 50$
    \item No noise and we assume the curve are sampled on a common grid.
    \item Based on the Karhunen-Loève decomposition, make sure that the decreasing of the eigenvalues is coherent with KL assumptions. The data are defined with a large number of components and different decreasing of the eigenvalues scenarios.
    \item We do the same for the percentage of variance explained. We set the percentage of variance explained for the multivariate components to be $\alpha\%$ ($\alpha = 50, 75, 90, 95, 99$) and we change the percentage of variance explained by the univariate components.
    \item The quality of the estimation is based on different measures: the number of retained components (only if we set the percentage of variance explained), the estimation of the eigenvalues ($\log-$AE), the estimation of the multivariate eigenfunctions (ISE) and the reconstruction of the curves (MISE).
    \item Data are simulated with \cite{happMultivariateFunctionalPrincipal2018a} setting and we can use ICHEC to run them.
\end{itemize}
% section introduction (end)